---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggdal

<!-- badges: start -->
[![R-CMD-check](https://github.com/hypertidy/ggdal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/ggdal/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ggdal is to get background image data for ggplot2. 


## Installation

You can install the development version of ggdal from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hypertidy/ggdal")
```

# Example


Use 'dsn = "osm"' or "virtualearth", or input custom (WIP). 

Use any map projection. Currently examples only provided for use with sf objects, WIP. 


```{r, example}
library(ggplot2)
library(ggdal)
data(iw)

ggplot() +
  annotation_gdal(dsn = "osm") +
  geom_sf(data = sf::st_transform(iw, "EPSG:3577"), fill = NA, col = "grey50")


ggplot() +
  annotation_gdal(dsn = "virtualearth") +
  geom_sf(data = sfdct::antarctica, fill = NA, col = "grey50") + coord_sf(xlim = c(-6378137, 6378137), 
                                                                          ylim = c(-6378137, 6378137))

```


## Code of Conduct
  
Please note that the ggdal project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
